Hector Permafrost

### 2020-03-17 analysis/paper/paper.Rmd
Use pkgload::load_all instead of devtools

```{r setup, echo = FALSE}
library(drake)
library(knitr)
library(here)
library(dplyr)
library(ggplot2)
library(hector.permafrost.emit)

@@

devtools::load_all("~/Projects/hector_project/hector-permafrost-submodel")

>>>>

```{r setup, echo = FALSE}
library(drake)
library(knitr)
library(here)
library(dplyr)
library(ggplot2)

@@

pkgload::load_all(here())
pkgload::load_all("~/Projects/hector_project/hector-permafrost-submodel")
